Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-20 documents/mixtures/mixture_models.tex
figure references
note to self
include tabular results

% to-do
% -----
% - make pickles_to_latex_table.py function
% - make figures showing use of the models in a real situation
% - does the Lupton paper give the profiles, or should we cite the code directly?
% - send to Jim Bosch and Kevin Bundy for comments
% - fix symbols on figures to match text or vice versa (K, M, v, sigma)

@@

The results of the optimizations are shown in the \tablename\ and
\figurename s... Discuss briefly the import of it all... Why in the
tables are we giving and plotting root-variances not variances?...

@@

\clearpage
\begin{table}
\caption{The amplitudes and root-variances for the best
  mixture-of-Gaussian approximations to the various profiles, for
  different mixture sizes.  The badness and total (dimensionless) flux
  are given for each approximation.}
\end{table}

>>>>

% to-do
% -----
% - add introduction comments about *why* people fit these profiles -- an opportunity to get on the soapbox
% - make pickles_to_latex_table.py function
% - make figures showing use of the models in a real situation
% - does the Lupton paper give the profiles, or should we cite the code directly?
% - send to Jim Bosch and Kevin Bundy for comments
% - fix symbols on figures to match text or vice versa (K, M, v, sigma)

@@

The results of the optimizations are shown in \tablename
s~\ref{tab:exp} through \ref{tab:luv} and \figurename s~\ref{fig:exp}
through \ref{fig:M}... Discuss briefly the import of it all... Why in
the tables are we giving and plotting root-variances not variances?...

@@

\clearpage
\begin{table}
\input{table_exp}
\caption{The amplitudes and root-variances for the best
  mixture-of-Gaussian approximations to the exp profile, for
  different mixture sizes.  The total (dimensionless) flux and the
  badness are given for each approximation.\label{tab:exp}}
\end{table}

\clearpage
\begin{table}
\input{table_dev}
\caption{Same as \tablename~\ref{tab:exp} but for the dev profile.}
\end{table}

\clearpage
\begin{table}
\input{table_lux}
\caption{Same as \tablename~\ref{tab:exp} but for the lux profile.}
\end{table}

\clearpage
\begin{table}
\input{table_luv}
\caption{Same as \tablename~\ref{tab:exp} but for the luv profile.\label{tab:luv}}
\end{table}
